---
output:
  word_document: default
  html_document: default
editor_options: 
  chunk_output_type: console
---
# Module 2 - Assignment 2

## Agyabeng, Prince

### Introduction to R Markdown

#### This is my first R Mardown documents

##### I will go over some of the topics I did in the previous module

###### Topics that will be covered include vectors, datatypes and dataframes.

###### The graph below will illustrate sales over six months.


```{r Plot of Sales by Month}
#==Question 2
library(tidyverse)
sales <- c(50, 150, 200, 100, 300, 250)
month <- c(1, 2, 3, 4, 5, 6)

###Creating scatterplot
qplot(month, sales)
```


###### What month had the largest sales? What was the amount? 5th month and 300


```{r Working with Data frames}
#==Question 4
Yearly_sales <- data.frame(months = c("Jan", "Feb", "March", "April", "May", "June", "July", "Aug", "Sept", "Oct", "Nov", "Dec"), sales = c(150.25, 258.54, 268.55, 122.52, 987, 458.82, 667.23, 845.54, 586.78, 888.58, 756.12, 456.84))
```


###### Which month had the most sales? The month of May

###### Which month had the least sales? The month of April