---
output:
  word_document: default
  html_document: default
---
#Module 4 - Assignment 1

##Agyabeng Prince

###Data Transformation

```{r}
library(tidyverse)

library(readr)
state_income <- read_csv("state_income.csv")
View(state_income)

```

####State Incomes

I will be creating a subset of data from the file

```{r}
State_income2 <- select(state_income,State_Name,State_ab,County,City,Type, ALand,Mean,Median, Stdev)

State_income2%>%select(State_ab, everything())

head(State_income2, n = 10)

```


```{r}
State_income2 <- rename(State_income2, SquareArea = ALand, IncomeMean = Mean, IncomeMedian = Median, IncomeStDev = Stdev)
head(State_income2)


```

```{r}
NC_Income <- filter(State_income2, State_Name == "North Carolina")
head(NC_Income, n = 10)

```


####NC Incomes
will be using the NC_income dataset to create summaries of the incomes within North Carolina including summaries by county, city and type.

```{r}
NC_Income_County <- arrange(NC_Income, County)
head(NC_Income_County, n = 10)
```


```{r}
summary1 <- group_by(NC_Income,County)
summary1 <- summarise (summary1, mean= mean(IncomeMean))
summary2 <- NC_Income %>%
group_by(City) %>%
summarise (mean = mean(IncomeMean))
```
The new data contains mean data income for the counties and mean income for the cities for North Carolina

```{r}
summary3 <- group_by(NC_Income,Type)
summary3 <- summarise (summary3, mean= mean(IncomeMean))
```


####Income Visualization

```{r}
library("tidyverse")

ggplot(summary1,aes(County, mean))+
  geom_point()+theme(axis.text.x = element_text(angle = 90,vjust =0.5, hjust=1))
  
```

