---
output:
  word_document: default
  html_document: default
---
#Module 5 - Assignment 1

##Agyabeng, Prince

###Data Wrangling

Part 1
```{r}
library(tidyverse)

library(readxl)
UN_migrant <- read_excel("UN_migrant.xlsx", 
    sheet = "Table 6", skip = 15)
View(UN_migrant)

```

Part 2 – Cleaning Data with dplyr

```{r}
UN_migrant <- rename(UN_migrant, Country = X__2, Country_code = X__4, Type = X__5, "1990" = "1990", "1995" = "1995")
head(UN_migrant)

Migration <- select(UN_migrant, Country, Country_code, Type, "1990", "1995", "2000", "2005", "2010", "2015")
head(Migration, n = 6)
```

### Part 3 – Creating tidy data using tidyr

```{r}
Migration2 <-Migration %>%
  gather('1990','1995','2000','2005','2010','2015',key='year', value='cases')
head(Migration2, n = 6)

Migration2$year <- as.integer(Migration2$year)
Migration2$cases <- as.integer(Migration2$cases)


```

###Part 4 – Research Questions

```{r}
##RegionalMigration %<%
  ##select(Migration2,Africa,Asia,Europe,Oceania,America) %<%
  ##filter(Country == "regions")


```

###Worldwide Migration based on Regions
a. Which region in the world had the highest number of migrants in the year 2005? Africa
b. Over the years, which region consistently has the most migrants every 5 year span? Which has the second most? Africa and Asia
c. What region has seen the fewest migrants over the years? South America
d. Which plot was most useful in answering these questions and why? bar graph because I can see the highest number.

  geom_point()+
```{r}
ggplot(Migration2,aes(year,cases,colors()))+
  labs(title = "Worldwide Migration", x = "Year", y = "Migration")

ggplot(Migration2, aes(year, cases))+
  geom_col()

```

